---
title: "How To Do This"
---

# Why Do This

Wanna see the file structure and language before installing? 

The underlying code for this site is hosted on GitHub:  

<https://github.com/EUV-student/homepage>

```{r, echo=F, warning=F, message=F}
library(webshot2)
webshot("https://github.com/EUV-student/homepage")
```

The landing page is `index.qmd`, inspect it in your browser: 

<https://github.com/EUV-student/homepage/blob/main/index.qmd>

```{r, echo=F, warning=F, message=F}
webshot("https://github.com/EUV-student/homepage/blob/main/index.qmd")
```

You see that `<center> text </center>` centers text and elements. 

The `iframe` tag comes straightforward from YouTube (right click embed code). 

If you like that, continue.

# How To Do This

- Install R: <https://cran.r-project.org/>
- Install RStudio: <https://posit.co/download/rstudio-desktop/>
- Install the quarto suite: <https://quarto.org/>
- Register GitHub: <https://github.com/>

Start RStudio. 

- Choose: File and New Project
- Choose: Project Type "Quarto Website"



