---
title: "Why Do This"
---

# Why Do This

It’s free. It’s challenging. It can be fun.

# What You Can Expected

Wanna see the file structure and language before installing? 

The homepage is a set of files. Each file can be opened with a text editor. 

The underlying code for this site is hosted on GitHub:  

<https://github.com/EUV-student/homepage>

```{r, echo=F, warning=F, message=F}
library(webshot2)
webshot("https://github.com/EUV-student/homepage")
```

The landing page is `index.qmd`, inspect it in your browser: 

<https://github.com/EUV-student/homepage/blob/main/index.qmd>

```{r, echo=F, warning=F, message=F}
webshot("https://github.com/EUV-student/homepage/blob/main/index.qmd")
```

You see that `<center> text </center>` centers text and elements. 

The `iframe` tag comes straightforward from YouTube (right click embed code). 

Styling works through markup languages. You can use `html` and `markdown`.

Other markup languages can be found in `LaTeX` or `Wikipedia`. 

If you like that, continue.
